---
title: "results"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Do celebrities have an advantage over KOLs (key opinion leader)? In particular, what’s the revenue comparison between the two groups? We have a hypothesis that people come to celebrities’ live streaming rooms because they like the person and come to KOLs’ live streaming rooms because KOLs offer a higher discount or have expertise in the specific area. 

```{r}
library(tidyverse)
library(lubridate)
library(ggrepel)

livestream <- read_csv("../processed data/Data_Livestream_General_processed.csv")
livestream

#change date
livestream$Date <- as.Date(livestream$Date,format='%m/%d/%y')
livestream$Host_category<-as.factor(livestream$Host_category)


#group revenue by day, host
total_by_day<-livestream %>% group_by(Name, Host_category, Date) %>%
  dplyr::summarize(Sales_amount_total = sum(Total_sales_amount,na.rm=TRUE),n=n()) %>%
  ungroup()

average<-total_by_day %>% group_by(Name, Host_category) %>%
  dplyr::summarize(Sales_amount_avg = mean(Sales_amount_total,na.rm=TRUE))  
  
total<-total_by_day %>% group_by(Name, Host_category) %>%
  dplyr::summarize(Sales_amount_total = sum(Sales_amount_total,na.rm=TRUE),n=n()) %>%
  left_join(average, by=c("Name", "Host_category"))
```

```{r}
#sales distribution: KOLs host more streaming than c; KOLs sell more than c
ggplot(total_by_day, aes(Sales_amount_total)) +
geom_histogram()+ 
facet_wrap(~Host_category)+
scale_x_continuous(labels = scales::comma)

#total number of days steaming: KOLs host more streaming than c
ggplot(total_by_day, aes(fct_infreq(Name), fill=Host_category)) +
geom_bar()+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

#total sales vs days of streaming: KOLs generate more revenue, Luo is an outlier
ggplot(total, aes(n, Sales_amount_total, color=Host_category)) +
geom_point()+
geom_label_repel(aes(label = Name), size = 2, min.segment.length = 0, max.overlaps = 9, show.legend=FALSE)

#avg sales vs days of streaming
ggplot(total, aes(n, Sales_amount_avg, color=Host_category)) +
geom_point()+
geom_label_repel(aes(label = Name), size = 2, min.segment.length = 0, max.overlaps = 9, show.legend=FALSE)+
scale_y_continuous(labels = scales::comma)
#jia nailiang just starts in mid-aug and only has two days of livestreaming. outlier

#after removing Jia: in general, celebrities hold less streaming and have more avg
total%>%filter(Name!='Jia Nailiang') %>%
ggplot(aes(n, Sales_amount_avg, color=Host_category)) +
geom_point()+
geom_label_repel(aes(label = Name), size = 2, min.segment.length = 0, max.overlaps = 9, show.legend=FALSE)+
scale_y_continuous(labels = scales::comma)

```


```{r}
#by categories
sales <-read_csv("../processed data/Data_Sales_processed2.csv")
sales
sum(is.na(sales))

#factor relevel
sales$Name<-as.factor(sales$Name)
name_order<-fct_reorder(total$Name,-total$Sales_amount_total)%>%levels()
sales$Name<-fct_relevel(sales$Name,name_order)
levels(sales$Name)


sales$Good_category_new<-as.factor(sales$Good_category_new)
sales_total<-sales %>% group_by(Good_category_new) %>%
  summarize(Sales_volume_total = sum(Sales_volume), Sales_amount_total = sum(Sales_amount))
good_order<-fct_reorder(sales_total$Good_category_new, -sales_total$Sales_amount_total)%>%levels()
sales$Good_category_new<-fct_relevel(sales$Good_category_new,good_order)
levels(sales$Good_category_new)

#aggregate ccategory total
sales2<-sales %>% group_by(Name,Host_category, Good_category_new) %>%
  summarize(Sales_volume_total = sum(Sales_volume), Sales_amount_total = sum(Sales_amount))


```

```{r}
#EDAV, not use
sales2%>%
ggplot(aes( Good_category_new,Name, fill=Sales_amount_total)) +
geom_tile()

#not use
ggplot(sales2, aes(x = Good_category_new, y = Sales_amount_total, color = Name)) +
  geom_point(size = 5, alpha = .5) +
  coord_flip() +
  facet_wrap(~Host_category, ncol = 1) 
 # scale_color_manual(values = icecreamcolors) +
  #theme_dotplot

#revenue by host, good category, not clear info
ggplot(sales2, aes(Sales_amount_total, Good_category_new,fill = Host_category)) + 
  geom_col() + 
  facet_wrap(~Name, nrow=4)+
  scale_x_continuous(labels = scales::comma)+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))+
  theme(legend.position = "top")
```

```{r}
sales2%>%
ggplot(aes( Good_category_new, Sales_amount_total, fill= Host_category)) +
geom_col(position = "dodge")+
scale_y_continuous(labels = scales::comma)+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

#K is generally good at 1 or 2 categories according to their expertise. 
sales2%>%
filter(Host_category=='K')%>%
  ggplot(aes(Good_category_new, Sales_amount_total)) + 
  geom_col(fill = 'red') + 
  facet_wrap(~Name, nrow=2)+
  scale_y_continuous(labels = scales::comma)+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))

#beauty is the most popular category in celebraies. Other categories is pretty even 
sales2%>%
filter(Host_category=='C')%>%
  ggplot(aes(Good_category_new,Sales_amount_total)) + 
  geom_col(fill = 'blue') + 
  facet_wrap(~Name, nrow=2)+
  scale_y_continuous(labels = scales::comma)+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))

```
From 2021/06 to 2021/08, among top20 hosts, KOL generated more revenue than celebrities.


Do celebrities have an advantage over KOLs (key opinion leader)? In particular, what’s the revenue comparison between the two groups? 
We have a hypothesis that people come to celebrities’ live streaming rooms because they like the person and come to KOLs’ live streaming rooms because KOLs offer a higher discount or have expertise in the specific area. 
We will focus on the top 20 hosts’ sales data in the past quarter to answer the questions. We will first define people to be celebrities if they are famous actors/actresses/singers based on our common judgments. Then we will look at their sales data and test our hypothesis.
look at sales in different cateogry

